\chapter{Project's current state} \label{cap:state}

The solution currently offers functionalities to:
\begin{itemize}
	\item Register and login users.
	
	\item Fill out a digital pre-donation form, that encompasses both the main questions of the form as well as relevant follow-up questions, that are triggered according to the user's responses.
	
	\item Manage the form's questions as well as the form's rules and manage users.
\end{itemize}

The project is currently experiencing some delays. These setbacks are primarily due to the inherent complexity of the project and our lack of knowledge in this particular domain.

One of the significant hurdles we have faced is the development of the backoffice's UI. Creating an intuitive and simple visual representation of both the form's questions and the underlying rules has proven to be particularly difficult. Ensuring that the user interface is both user-friendly and accurately reflects the complexity of the rules involved has required substantial effort and ongoing iterative refinement.

Furthermore, we remain committed to delivering a solution that will automatically verify drug and pathology interactions with blood donations. Although this feature is optional, it has the potential to significantly enhance the blood donation procedure. However, the lack of easily accessible, machine-readable information from the IPST manual has posed a significant challenge. Extracting and integrating this critical data in a way that ensures accuracy and reliability has been a complex task.
